Subsegmental language detection in Celtic language text

### 2014-06-27 codeswitch-cltw-2014/codeswitch_camera_ready.tex
evaluation review 1.4
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55020 72bbbca6-d526-0410-a7d9-f06f51895060

We hand-annotated a small evaluation set from a selection of posts to a popular microblogging site\footnote{\url{http://indigenoustweets.blogspot.in/2013/12/mapping-celtic-twittersphere.html}}. The posts `tweets' were filtered into three sets which had been identified as Irish, Welsh and Breton.  Certain tokens were escaped from the data, such as mentioned (which are preceded by an \texttt{@} symbol), subject tags `hashtags' which are preceded by a \texttt{\#} symbol), hyperlinks and the sequence \texttt{rt} which stands for `re-tweet'. An example of the content of our corpus after annotation is given in Figure~\ref{fig:tweets}. All of the tweets had at least one instance of code-switching.

@@

\begin{figure}
\begin{small}
\begin{alltt}
[\textbf{en} You're a] [\textbf{ga} Meirice\'{a}nach, c\'{e}n f\'{a}th] [\textbf{en} are you] [\textbf{ga} foghlaim Gaeilge?!] 
@afaltomkins [\textbf{cy} gorfod cael bach o tan] [\textbf{en} though init] 
[\textbf{en} omg] [\textbf{cy} mar cwn bach yn] [\textbf{en} black and tan] [\textbf{cy} a popeth,] [\textbf{en} even cuter!!] 
\end{alltt}
\end{small}
\caption{Example of text from a microblogging site chunked}
\label{fig:tweets}
\end{figure}

>>>>

We hand-annotated a small evaluation set from a selection of posts to a popular microblogging site\footnote{\url{http://indigenoustweets.blogspot.in/2013/12/mapping-celtic-twittersphere.html}}. The posts `tweets' were filtered into three sets which had been identified as Irish, Welsh and Breton.  Certain tokens were escaped from the data, such as mentioned (which are preceded by an \texttt{@} symbol), subject tags `hashtags' which are preceded by a \texttt{\#} symbol), hyperlinks and the sequence \texttt{rt} which stands for `re-tweet'. An example of the content of our corpus after hand annotation is given in Figure~\ref{fig:tweets}. All of the tweets had at least one instance of code-switching.

@@

\begin{figure}
\begin{small}
\begin{alltt}
[\textbf{en} You're a] [\textbf{ga} Meirice\'{a}nach, c\'{e}n f\'{a}th] [\textbf{en} are you] [\textbf{ga} foghlaim Gaeilge?!] 
@afaltomkins [\textbf{cy} gorfod cael bach o tan] [\textbf{en} though init] 
[\textbf{en} omg] [\textbf{cy} mar cwn bach yn] [\textbf{en} black and tan] [\textbf{cy} a popeth,] [\textbf{en} even cuter!!] 
\end{alltt}
\end{small}
\caption{Example of text from a microblogging site chunked manually.}
\label{fig:tweets}
\end{figure}
